---
title: "Simulation study"
output: html_notebook
---


```{r setup}
source('R/SPreg.R', echo=FALSE)

```

Goal:

 * simulate data with a q-power backbone distribution that follows the relative-risk regression model
 * fit the data using our semi-parametric regression model, beta-binomial regression (misspecified correlation structure), and GEE (marginal only)
 
 
$$
	\lambda_k(z) = {\mu_k} \times {\theta(\beta' z)^k}, k = 0, \dots, K,
$$

## Simulating data
### Cluster-size distributions

 1. All small (3); 
 2. All large (10); 
 3. varying (0.5*(1+binom(9, 0.5)) + 0.5*Unif(2,10))

```{r Clustersizes}
cs.small <- function(n) rep(3, n)
cs.large <- function(n) rep(10, n)
cs.varied <- function(n) {
  p <- rbinom(n, size=1, prob=0.5)
  x <- ifelse(p, 1+rbinom(n, size=9, prob=0.5), sample(2:10, size=n, replace=TRUE))
  x
}
```

### Simulate one dataset

The inputs will be

 * `n` - number of clusters to simulate data
 * `clustersize.gen` - function to generate the clustersizes
 * `backbone.gen` - function to generate the PDF of the backbone
 * `covariate.gen` - function to generate the covariates
 * `beta` - coefficients of the linear predictor
 * `link` - the link-function for the semi-parametric model; the inverse link is the $\theta$ function in the equation

```{r SimSetup}
sim.sp <- function(n, clustersize.gen, backbone.gen, 
                   covariate.gen, beta, link="cloglog"){
  
   model_fun <- binomial(link=link)$linkinv
   
   cs <- clustersize.gen(n)
   K <- max(cs)
   cov.mat <- covariate.gen(n)
   
   lp <- cov.mat %*% beta
   theta <- model_fun(lp)
   
   q0 <- backbone.gen(K)
   lambda0 <- lambda_from_p(q0)
   
   th <- sapply(0:R, function(k)theta^k)
   lambda <- apply(th, 1, function(t)t * lambda0)
   rownames(lambda) <- 0:R
   
   q <- lapply(1:n,
               function(idx)p_from_lambda(lambda[,idx], n=cs[idx]))
   nresp <- lapply(q, function(qq)sample(seq_along(qq)-1, 
                                         size=1, prob=qq))
   res <- data.frame(ID=1:n,
                     ClusterSize = cs,
                     NResp = nresp)
   res <- cbind(res, cov.mat)
   res
}   
  
```

 
 
 